\LARGE \bf Mean Estimation from One-Bit Measurements

### 2022-05-02 distributed-estimation.tex
example for A2-(ii)

\subsection{Optimal Efficiency}
We begin by making a few restrictions on the collections of the sets $A_i$,
which we believe not unreasonable, but which allow us to develop fundamental
limits for estimation. We require a bit of notation to define the
assumptions. As we work with a location family based on a density $f$
with associated probability distribution $P$ on variables $Z$,
we define
\begin{equation*}
  P_\theta(A) \defeq P(Z - \theta \in A)
\end{equation*}
for $Z$ with density $f$. Whenever $A$ is a collection of disjoint intervals $A = \cup_i [t_i^-, t_i^+]$, we may define
\begin{equation*}
  \dPtheta(A) \defeq \frac{\partial}{\partial \theta} P_\theta(A)
  = \sum_i \left(f(t_i^- - \theta) - f(t_i^+ - \theta)\right),
\end{equation*}
and similarly we define the score
function $\score_\theta(A) \defeq \dPtheta(A) / P_\theta(A)$.
For $B = \indic{X \in A}$, we abuse notation and also write
$\score_\theta(B) = \score_\theta(A)$ and similarly for $\dPtheta$.
With this, we may define the variance of the
scores $\score_\theta(B_i)$ under $P_\theta$ via
\begin{equation}
  \label{eq:precision_general}
  L_n(A_1,\ldots,A_n;\theta) \defeq
  \frac{1}{n} \sum_{i=1}^n \frac{ \dPtheta(A_i)^2}{
    P_\theta(A_i) (1 - P_\theta(A_i))}.
\end{equation}
We then make the following assumption.
\begin{assumption}
  \label{assumption:detection-regions}
  The density and detection regions satisfy
  \begin{enumerate}[(i)]
  \item \label{item:lipschitz-density}
    The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
  \item \label{item:finite-intervals}
    Each set $A_i$ is the finite union of $k_i$ disjoint intervals
    (which may include $\pm \infty$), where
    \begin{equation*}
      \frac{1}{n} \cdot \max_{i \le n} \frac{k_i^3}{P_\theta(A_i)^4
        (1 - P_\theta(A_i))^4} \to 0.
    \end{equation*}
  \item \label{item:limit-variance}
    The limit
    \begin{equation}
      \label{eqn:LAN-limit}
      \kappa(\theta) \defeq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
    \end{equation}
    exists and is finite.
  \end{enumerate}
\end{assumption}
Roughly speaking, \eqref{item:finite-intervals} above holds whenever the intervals consisting each $A_i$ are appropriately seperated. For example, it applies when each set $A_i$ is a half-bounded interval $(t_i,\infty)$ with $\min\{P_\theta((t_i,\infty)), P_\theta((-\infty,t_i])\} = \omega(1/n)$ as we dicscuss in more detail below. More generally, suppose that $A_i = \cup_{j=1}^{k_i}[t_{i,j}^-, t_{i,j}^+]$ and let 
\begin{align*}
c_n^+ & =  \min_{i \le n} \min_{j \leq k_i}  F(t^+_{i,j} - \theta) - F(t^-_{i,j}- \theta) \\
c_n^- & = \min_{i \le n} \min_{j \leq k_i}  F(t^-_{i,j+1}- \theta)  - F(t^+_{i,j}- \theta),
\end{align*}
with $t^-_{i,k_i+1} = \infty$. Then Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $\max_{i \le n} k_i^3 (c_n^- c_n^+)^4 = o(n)$.

>>>>

\subsection{Optimal Efficiency}
We begin by making a few restrictions on the collections of the sets $A_i$,
which we believe not unreasonable, but which allow us to develop fundamental
limits for estimation. We require a bit of notation to define the
assumptions. As we work with a location family based on a density $f$
with associated probability distribution $P$ on variables $Z$,
we define
\begin{equation*}
  P_\theta(A) \defeq P(Z - \theta \in A)
\end{equation*}
for $Z$ with density $f$. Whenever $A$ is a collection of disjoint intervals $A = \cup_i [t_i^-, t_i^+]$, we may define
\begin{equation*}
  \dPtheta(A) \defeq \frac{\partial}{\partial \theta} P_\theta(A)
  = \sum_i \left(f(t_i^- - \theta) - f(t_i^+ - \theta)\right),
\end{equation*}
and similarly we define the score
function $\score_\theta(A) \defeq \dPtheta(A) / P_\theta(A)$.
For $B = \indic{X \in A}$, we abuse notation and also write
$\score_\theta(B) = \score_\theta(A)$ and similarly for $\dPtheta$.
With this, we may define the variance of the
scores $\score_\theta(B_i)$ under $P_\theta$ via
\begin{equation}
  \label{eq:precision_general}
  L_n(A_1,\ldots,A_n;\theta) \defeq
  \frac{1}{n} \sum_{i=1}^n \frac{ \dPtheta(A_i)^2}{
    P_\theta(A_i) (1 - P_\theta(A_i))}.
\end{equation}
We then make the following assumption.
\begin{assumption}
  \label{assumption:detection-regions}
  The density and detection regions satisfy
  \begin{enumerate}[(i)]
  \item \label{item:lipschitz-density}
    The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
  \item \label{item:finite-intervals}
    Each set $A_i$ is the finite union of $k_i$ disjoint intervals
    (which may include $\pm \infty$), where
    \begin{equation*}
      \frac{1}{n} \cdot \max_{i \le n} \frac{k_i^3}{P_\theta(A_i)^4
        (1 - P_\theta(A_i))^4} \to 0.
    \end{equation*}
  \item \label{item:limit-variance}
    The limit
    \begin{equation}
      \label{eqn:LAN-limit}
      \kappa(\theta) \defeq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
    \end{equation}
    exists and is finite.
  \end{enumerate}
\end{assumption}
Roughly speaking, \eqref{item:finite-intervals} above holds whenever the intervals consisting each $A_i$ are appropriately seperated and their number is relatively small. For example, it applies when each set $A_i$ is a half-bounded interval $(t_i,\infty)$ with $\min\{P_\theta((t_i,\infty)), P_\theta((-\infty,t_i])\} = \omega(1/n)$ as we dicscuss in more detail below. More generally, let $\Delta_i$ the minimal distance between any two interval endpoints in $A_i$. Then, 
if $A_i = \cup_{j=1}^{k_i}[t_{i,j}^-, t_{i,j}^+]$, we have that 
$P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $1-P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^+)$. Therefore, As long as $\sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $\sum_{j=1}^{k_i} F(t_{i,j}^+)$ are bounded away from zero, \ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $ \max_{i \le n} k_i^3 \Delta_i^{-4} = o(n)$.
